Housing Default Handovers

### 2024-10-09 minos/validation/handovers.Rmd
grepping sf12 to sf12_mcs. and sf12_mcs_pcs to sf12_pcs

```{r}
# Read raw datafiles in
#raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.files <- list.files(here::here('data', 'imputed_final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
#raw.files <- list.files(here::here('data', 'scaled_scotland_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
raw.dat <- raw.dat %>%
  filter(weight > 0)

out.path <- here::here('output', 'default_config/')
# out.path <- here::here('output', 'scotland_scaled/')
base.dat <- read_singular_local_out(out.path, 'baseline',
                                    drop.dead = TRUE,
                                    drop.zero.weight = TRUE)

# base.dat <- read_singular_local_out(out.path, 'ChildPovertyReduction',
#                                     drop.dead = TRUE,
#                                     drop.zero.weight = TRUE)

#base.dat <- read_singular_local_out(out.path, 'goodHeatingDummy', drop.dead = TRUE)
```

@@

```{r}
# Having a go at an age pyramid, hopefully animated

brks = c(75, 80, 85, 90, 95, 100, 105, 110)
lbls = c("75to80", "80to85", "85to90", "90to95", "95to100", "100to105", "105to110")

var <- 'age_group'

# start with calculating percentages
#raw.oldAgePct
#base.oldAgePct

raw.oldAgePct <- raw.dat %>%
  filter(age > 75) %>%
  mutate(age_group = cut(age,
                         breaks = brks,
                         labels = lbls)) %>%
  dplyr::select(time, age_group) %>%
  group_by(time, age_group) %>%
  count() %>%
  mutate(source = 'predicted')

base.oldAgePct <- base.dat %>%
  filter(age > 75) %>%
  mutate(age_group = cut(age,
                         breaks = brks,
                         labels = lbls)) %>%
  dplyr::select(time, all_of(var)) %>%
  #filter(!.data[[var]] %in% miss.values) %>%
  group_by(time, .data[[var]]) %>%
  count() %>%
  mutate(source = 'observed')

raw.oldAgePct[[var]] <- as.factor(raw.oldAgePct[[var]])
base.oldAgePct[[var]] <- as.factor(base.oldAgePct[[var]])

merged <- rbind(raw.oldAgePct, base.oldAgePct)
merged[[var]] <- as.factor(merged[[var]])

var.norm <- merged %>%
    group_by(time) %>%
    mutate(total = sum(n)) %>%
    mutate(prct = (n / total) * 100)
```

## Population Counts

### Total Pop

```{r}
raw.alive <- raw.dat %>%
  group_by(time) %>%
  summarise(n = n()) %>%
  mutate(scen = 'final_US')

base.alive <- base.dat %>%
  group_by(time) %>%
  summarise(n = n()) %>%
  mutate(scen = 'baseline')

#handover_boxplots(raw.alive, base.alive, 'n')
#handover_lineplots(raw.alive, base.alive, "n")

combined <- rbind(raw.alive, base.alive)

ggplot(combined, aes(x = time, y = n, group = scen, color = scen, fill = scen)) +
  geom_line() +
  geom_vline(xintercept = start.year, linetype = 'dashed') +
  labs(title = 'Total Count in Sample') +
  xlab('Year') +
  ylab('Count')

rm(raw.alive, base.alive)
```

### Households

```{r}
raw.hhs <- raw.dat %>%
  select(hidp, time) %>%
  distinct() %>%
  group_by(time) %>%
  summarise(n = n()) %>%
  mutate(source = 'final_US')

base.hhs <- base.dat %>%
  select(hidp, time) %>%
  distinct() %>%
  group_by(time) %>%
  summarise(n = n()) %>%
  mutate(source = 'baseline')

combined <- rbind(raw.hhs, base.hhs)

ggplot(combined, aes(x = time, y = n, group = source, color = source, fill = source)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = start.year, linetype = 'dashed') +
  labs(title = 'Households Count')
```

### Households With Children

```{r}
raw.household_count_by_year <- raw.dat %>%
  filter(nkids > 0) %>%
  select(hidp, time) %>%  # Select relevant columns to reduce data size
  distinct() %>%
  group_by(time) %>%
  summarise(n = n()) %>%
  mutate(source = 'final_US')

base.household_count_by_year <- base.dat %>%
  filter(nkids > 0) %>%
  select(hidp, time) %>%  # Select relevant columns to reduce data size
  distinct() %>%
  group_by(time) %>%
  summarise(n = n()) %>%
  mutate(source = 'baseline')

combined <- rbind(raw.household_count_by_year, base.household_count_by_year)

ggplot(combined, aes(x = time, y = n, group = source, color = source, fill = source)) +
  geom_point() +
  geom_line() +
  labs(title = 'Households with Children Count')
```

### Households With Children (Income Quintile)

```{r}
raw.hhs_kids.income_quint <- raw.dat %>%
  filter(nkids > 0) %>%
  select(hidp, time, hh_income) %>%  # Select relevant columns to reduce data size
  distinct() %>%
  mutate(income_group = case_when(
    hh_income <= 1000 ~ "<= 1000",
    hh_income <= 1500 ~ "1001 - 1500",
    hh_income <= 2000 ~ "1501 - 2000",
    hh_income <= 2500 ~ "2001 - 2500",
    hh_income > 2500  ~ "> 2500"
  )) %>%
  group_by(time, income_group) %>%
  summarise(n = n(), .groups = 'drop') %>%
  mutate(source = 'final_US')

base.hhs_kids.income_quint <- base.dat %>%
  filter(nkids > 0) %>%
  select(hidp, time, hh_income) %>%  # Select relevant columns to reduce data size
  distinct() %>%
  mutate(income_group = case_when(
    hh_income <= 1000 ~ "<= 1000",
    hh_income <= 1500 ~ "1001 - 1500",
    hh_income <= 2000 ~ "1501 - 2000",
    hh_income <= 2500 ~ "2001 - 2500",
    hh_income > 2500  ~ "> 2500"
  )) %>%
  group_by(time, income_group) %>%
  summarise(n = n(), .groups = 'drop') %>%
  mutate(source = 'baseline')

combined <- rbind(raw.hhs_kids.income_quint, base.hhs_kids.income_quint)
combined$income_group <- factor(combined$income_group)

ggplot(combined, aes(x = time, y = n, group = income_group, color = income_group, fill = income_group)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = start.year) +
  labs(title = 'Households with Children Count')
```

#### Proportions

```{r}
calculate_hh_proportions <- function(data) {
  # Step 1: Filter for households with children
  households_with_kids <- data %>%
    filter(nkids > 0) %>%
    select(hidp, time, hh_income) %>%
    distinct()

  # Step 2: Create income group based on thresholds
  households_with_kids <- households_with_kids %>%
    mutate(income_group = case_when(
      hh_income <= 1000 ~ "<= 1000",
      hh_income <= 1500 ~ "1001 - 1500",
      hh_income <= 2000 ~ "1501 - 2000",
      hh_income <= 2500 ~ "2001 - 2500",
      hh_income > 2500  ~ "> 2500"
    ))

  # Step 3: Count households within each income group per year
  household_counts <- households_with_kids %>%
    group_by(time, income_group) %>%
    summarise(count = n(), .groups = 'drop')

  # Step 4: Calculate total households with children per year
  total_households_per_year <- households_with_kids %>%
    group_by(time) %>%
    summarise(total_count = n(), .groups = 'drop')

  # Step 5: Calculate proportion of households in each group per year
  household_proportions <- household_counts %>%
    left_join(total_households_per_year, by = "time") %>%
    mutate(proportion = count / total_count) %>%
    select(time, income_group, proportion)

  return(household_proportions)
}

raw.hh_kids_prop <- calculate_hh_proportions(raw.dat)
base.hh_kids_prop <- calculate_hh_proportions(base.dat)

raw.hh_kids_prop$source <- 'final_US'
raw.hh_kids_prop <- filter(raw.hh_kids_prop, time != start.year)
base.hh_kids_prop$source <- 'baseline'

combined <- rbind(raw.hh_kids_prop, base.hh_kids_prop)
combined$income_group <- factor(combined$income_group)

ggplot(combined, aes(x = time, y = proportion, group = income_group, color = income_group, fill = income_group)) +
  geom_col() +
  geom_vline(xintercept = start.year) +
  labs(title = 'Households with Children Count')
```

```{r}
# # Step 1: Filter for households with children
# households_with_kids <- raw.dat %>%
#   filter(nkids > 0) %>%
#   select(hidp, time, hh_income) %>%
#   distinct() %>%
#   select(-hidp)
# 
# # Step 2: Calculate income quintiles
# households_with_kids <- households_with_kids %>%
#   group_by(time) %>%
#   mutate(income_quintile = ntile(hh_income, 5)) %>%
#   ungroup()
# 
# # Step 3: Count households within each income quintile per year
# household_count_by_income_quintile <- households_with_kids %>%
#   group_by(time, income_quintile) %>%
#   summarise(n = n())
# 
# household_count_by_income_quintile
```

### Households With Children (Ethnic Group)

```{r}
raw.hhs_kids.ethnicity <- raw.dat %>%
  filter(nkids > 0) %>%
  select(hidp, time, hh_income, ethnicity) %>%  # Select relevant columns to reduce data size
  distinct() %>%
  group_by(time, ethnicity) %>%
  summarise(n = n(), .groups = 'drop') %>%
  mutate(source = 'final_US')

base.hhs_kids.ethnicity <- base.dat %>%
  filter(nkids > 0) %>%
  select(hidp, time, hh_income, ethnicity) %>%  # Select relevant columns to reduce data size
  distinct() %>%
  group_by(time, ethnicity) %>%
  summarise(n = n(), .groups = 'drop') %>%
  mutate(source = 'baseline')

combined <- rbind(raw.hhs_kids.ethnicity, base.hhs_kids.ethnicity)
combined$ethnicity <- factor(combined$ethnicity)

ggplot(combined, aes(x = time, y = n, group = ethnicity, color = ethnicity, fill = ethnicity)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = start.year) +
  labs(title = 'Households with Children Count')
```

```{r}
calculate_hh_proportions <- function(data, group.var) {
  # Step 1: Filter for households with children
  households_with_kids <- data %>%
    filter(nkids > 0) %>%
    select(hidp, time, hh_income, .data[[group.var]]) %>%
    distinct()

  # Step 3: Count households within each income group per year
  household_counts <- households_with_kids %>%
    group_by(time, .data[[group.var]]) %>%
    summarise(count = n(), .groups = 'drop')

  # Step 4: Calculate total households with children per year
  total_households_per_year <- households_with_kids %>%
    group_by(time) %>%
    summarise(total_count = n(), .groups = 'drop')

  # Step 5: Calculate proportion of households in each group per year
  household_proportions <- household_counts %>%
    left_join(total_households_per_year, by = "time") %>%
    mutate(proportion = count / total_count) %>%
    select(time, .data[[group.var]], proportion)

  return(household_proportions)
}

raw.hh_kids_prop <- calculate_hh_proportions(raw.dat, group.var = 'ethnicity')
base.hh_kids_prop <- calculate_hh_proportions(base.dat, group.var = 'ethnicity')

raw.hh_kids_prop$source <- 'final_US'
raw.hh_kids_prop <- filter(raw.hh_kids_prop, time != start.year)
base.hh_kids_prop$source <- 'baseline'

combined <- rbind(raw.hh_kids_prop, base.hh_kids_prop)
combined$ethnicity <- factor(combined$ethnicity)

ggplot(combined, aes(x = time, y = proportion, group = ethnicity, color = ethnicity, fill = ethnicity)) +
  geom_col() +
  geom_vline(xintercept = start.year) +
  labs(title = 'Households with Children Count')
```

@@

```{r}
# sf12 boxplot handovers
handover_boxplots(raw.dat, base.dat, 'SF_12')
handover_lineplots(raw.dat, base.dat, "SF_12")

handover_boxplots(raw.dat, base.dat, 'SF_12_diff')
handover_lineplots(raw.dat, base.dat, "SF_12_diff")

@@

```{r}
raw.sf12 <- raw.dat %>%
  select(pidp, age, time, SF_12, SF_12_diff)
base.sf12 <- base.dat %>%
  select(pidp, age, time, SF_12, SF_12_diff)

@@

sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
spaghetti_plot(sf12.spag.sample, 'SF_12',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12',
               save = shall.we.save,
               save.path = save.path)

spaghetti_plot(sf12.spag.sample, 'SF_12_diff',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12_diff',
               save = shall.we.save,
               save.path = save.path)

density_ridges(sf12.spag, "SF_12", 
               save = T, 
               save.path = save.path)

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, housing_quality)
base.s <- base.dat %>%
  select(pidp, age, time, housing_quality)

spaghetti_plot(spag, 'housing_quality',
               save = shall.we.save,
               save.path = save.path)

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, neighbourhood_safety)
base.s <- base.dat %>%
  select(pidp, age, time, neighbourhood_safety)

spaghetti_plot(spag, 'neighbourhood_safety',
               save = shall.we.save,
               save.path = save.path)

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, education_state)
base.s <- base.dat %>%
  select(pidp, age, time, education_state)

spaghetti_plot(spag, 'education_state',
               save = shall.we.save,
               save.path = save.path)

## Behind On Bills

```{r}
raw.behind_on_bills <- raw.dat %>%
  dplyr::select(pidp, time, behind_on_bills) %>%
  group_by(time, behind_on_bills) %>%
  count() %>%
  mutate(source = 'final_US')

base.behind_on_bills <- base.dat %>%
  dplyr::select(pidp, time, behind_on_bills) %>%
  group_by(time, behind_on_bills) %>%
  count() %>%
  mutate(source = 'baseline_output')

# merge before plot
behind_on_bills <- rbind(raw.behind_on_bills, base.behind_on_bills)
behind_on_bills$behind_on_bills <- as.factor(behind_on_bills$behind_on_bills)

# Now plot
ggplot(data = behind_on_bills, mapping = aes(x = time, y = n, group = behind_on_bills, colour = behind_on_bills)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Behind On Bills', subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

behind_on_bills.norm <- behind_on_bills %>%
  group_by(time) %>%
  mutate(total = sum(n)) %>%
  mutate(prct = (n / total))

ggplot(data = behind_on_bills.norm, mapping = aes(x = time, y = prct, fill=behind_on_bills)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Behind On Bills') +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'behind_on_bills.png',
       plot = last_plot(),
       path = save.path)
}

rm(raw.behind_on_bills, base.behind_on_bills, behind_on_bills, behind_on_bills.norm)
```

>>>>

# Read raw datafiles in
#raw.files <- list.files(here::here('data', 'imputed_final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.files <- list.files(here::here('data', 'scaled_manchester_aligned_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

out.path <- here::here('output', 'energy_default_config/')
out.path <- here::here('output', 'energy_manchester_scaled/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
```

@@

@@

```{r}
# sf12 boxplot handovers
handover_boxplots(raw.dat, base.dat, 'SF_12_MCS')
handover_lineplots(raw.dat, base.dat, "SF_12_MCS")
# 
# raw.sf12 <- raw.dat %>% 
#   dplyr::select(pidp, time, SF_12_MCS) %>%
#   group_by(time) %>%
#   summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
#   mutate(source = 'final_US')
# 
# base.sf12 <- base.dat %>%
#   dplyr::select(pidp, time, SF_12_MCS) %>%
#   group_by(time) %>%
#   summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
#   mutate(source = 'baseline_output')
# 
# # merge before plot
# sf12 <- rbind(raw.sf12, base.sf12)
# 
# # Now plot
# ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
#   geom_smooth() +
#   #geom_line() +
#   geom_vline(xintercept=start.year, linetype='dotted') +
#   labs(title = 'Mental Wellbeing (SF12)', subtitle = 'Full Sample') +
#   xlab('Year') +
#   ylab('SF12')
# 
# ## Try a version where final_US is limited to only those present from wave 1 
# # onwards because the sample refreshments are messing with the plot
# raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
# 
# raw.sf12.2 <- raw.dat %>% 
#   dplyr::select(pidp, time, SF_12_MCS) %>%
#   filter(pidp %in% raw.sf12.wave1) %>%
#   group_by(time) %>%
#   summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
#   mutate(source = 'final_US')
# 
# base.sf12.2 <- base.dat %>%
#   dplyr::select(pidp, time, SF_12_MCS) %>%
#   filter(pidp %in% raw.sf12.wave1) %>%
#   group_by(time) %>%
#   summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
#   mutate(source = 'baseline_output')
# 
# sf12.2 <- rbind(raw.sf12.2, base.sf12.2)
# 
# # Now plot
# ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
#   geom_line() +
#   geom_vline(xintercept=start.year, linetype='dotted') +
#   labs(title = 'Mental Wellbeing (SF12 MCS)') +
#   xlab('Year') +
#   ylab('SF12')
# 
# if (shall.we.save) {
#   ggsave(filename = 'SF12_wav1.png',
#        plot = last_plot(),
#        path = save.path)
# }
# 
# rm(raw.sf12, base.sf12, sf12, raw.sf12.wave1, raw.sf12.2, base.sf12.2, sf12.2)
```

@@

```{r}
raw.sf12 <- raw.dat %>%
  select(pidp, age, time, SF_12_MCS)
base.sf12 <- base.dat %>%
  select(pidp, age, time, SF_12_MCS)

@@

sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
spaghetti_plot(sf12.spag.sample, 'SF_12_MCS',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12_MCS',
               save = shall.we.save,
               save.path = save.path)

density_ridges(sf12.spag, "SF_12_MCS", 
               save = T, 
               save.path = save.path)

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, housing_quality)
# base.s <- base.dat %>%
#   select(pidp, age, time, housing_quality)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'housing_quality',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

## Housing Tenure

```{r}
raw.tenure <- raw.dat %>%
  dplyr::select(pidp, time, housing_tenure) %>%
  group_by(time, housing_tenure) %>%
  count() %>%
  mutate(source = 'final_US')

base.tenure <- base.dat %>%
  dplyr::select(pidp, time, housing_tenure) %>%
  group_by(time, housing_tenure) %>%
  count() %>%
  mutate(source = 'baseline_output')

# merge before plot
tenure <- rbind(raw.tenure, base.tenure)
tenure$housing_tenure <- as.factor(tenure$housing_tenure)

# Now plot
ggplot(data = tenure, mapping = aes(x = time, y = n, group = housing_tenure, colour = housing_tenure)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Housing Tenure', subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

tenure.norm <- tenure %>%
  group_by(time) %>%
  mutate(total = sum(n)) %>%
  mutate(prct = (n / total))

ggplot(data = tenure.norm, mapping = aes(x = time, y = prct, fill=housing_tenure)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Housing Tenure') +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'housing_tenure.png',
       plot = last_plot(),
       path = save.path)
}

rm(raw.tenure, base.tenure, tenure, tenure.norm)
```

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, neighbourhood_safety)
# base.s <- base.dat %>%
#   select(pidp, age, time, neighbourhood_safety)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'neighbourhood_safety',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, education_state)
# base.s <- base.dat %>%
#   select(pidp, age, time, education_state)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'education_state',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

### 2024-10-09 minos/validation/housing_handovers.Rmd
grepping sf12 to sf12_mcs. and sf12_mcs_pcs to sf12_pcs

```{r}
# sf12 boxplot handovers
handover_boxplots(raw.dat, base.dat, 'SF_12')
handover_lineplots(raw.dat, base.dat, "SF_12")

raw.sf12 <- raw.dat %>%
  dplyr::select(pidp, time, SF_12) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12 <- base.dat %>%
  dplyr::select(pidp, time, SF_12) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

raw.sf12.2 <- raw.dat %>%
  dplyr::select(pidp, time, SF_12) %>%
  filter(pidp %in% raw.sf12.wave1) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12.2 <- base.dat %>%
  dplyr::select(pidp, time, SF_12) %>%
  filter(pidp %in% raw.sf12.wave1) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

```{r}
raw.sf12 <- raw.dat %>%
  select(pidp, age, time, SF_12)
base.sf12 <- base.dat %>%
  select(pidp, age, time, SF_12)

@@

sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
spaghetti_plot(sf12.spag.sample, 'SF_12',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12',
               save = shall.we.save,
               save.path = save.path)

density_ridges(sf12.spag, "SF_12",
               save = T,
               save.path = save.path)

>>>>

```{r}
# sf12 boxplot handovers
handover_boxplots(raw.dat, base.dat, 'SF_12_MCS')
handover_lineplots(raw.dat, base.dat, "SF_12_MCS")

raw.sf12 <- raw.dat %>%
  dplyr::select(pidp, time, SF_12_MCS) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12 <- base.dat %>%
  dplyr::select(pidp, time, SF_12_MCS) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

raw.sf12.2 <- raw.dat %>%
  dplyr::select(pidp, time, SF_12_MCS) %>%
  filter(pidp %in% raw.sf12.wave1) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12.2 <- base.dat %>%
  dplyr::select(pidp, time, SF_12_MCS) %>%
  filter(pidp %in% raw.sf12.wave1) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

@@

```{r}
raw.sf12 <- raw.dat %>%
  select(pidp, age, time, SF_12_MCS)
base.sf12 <- base.dat %>%
  select(pidp, age, time, SF_12_MCS)

@@

sf12.spag.sample <- sf12.spag[which(sf12.spag$pidp %in% pidp_sample), ]
spaghetti_plot(sf12.spag.sample, 'SF_12_MCS',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(sf12.spag.sample, 'SF_12_MCS',
               save = shall.we.save,
               save.path = save.path)

density_ridges(sf12.spag, "SF_12_MCS",
               save = T,
               save.path = save.path)
